Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-09-30 files/Chapter7/Introduction.tex
intro change

Section 7.2 is a discussion and a replication of numerical results of the work done in the article \cite{LVV09}. In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam. Extra results are included in this section to verify the conclusions of the authors of \cite{LVV09}. The results of this section are also used as a reference for the rest of the chapter.

>>>>

Section 7.2 is a discussion of the work and a replication of numerical results of/ the article \cite{LVV09}. In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam. The results of this section are also used as a reference for the rest of the chapter.
